### 2014-09-09 Procedure.tex
first stats figures; n_p,q renamed to n_P,Q

The final fourth step consists of reconstructing the equilibria form synthetic FREEBIE data using EFIT++ and VacTH. The reconstructions are then compared to the original equilibrium, focusing on global parameters and geometry. VacTH does not provide a full equilibrium but the plasma shape only (the target of VacTH is to provide such reconstructions in real time for a feedback control). Scans are performed over noise levels ($\epsilon$) and selected code parameters: $p'$ and $FF'$ polynomial degrees in EFIT++ ($n_{p'}$, $n_{FF'}$) and the number of harmonics ($n_{\mathrm p}$, $n_{\mathrm q}$) in VacTH. The following quantities are used for the comparison.
\begin{table}[!h]
    \begin{tabular}{ll}
    $R_{\mathrm ax}$, $Z_{\mathrm ax}$ & $R,Z$ coordinates of the magnetic axis \\
    $R_{\mathrm in}$, $R_{\mathrm out}$ & inner/outer $R$ coordinate of LCFS at $Z=Z_{\mathrm ax}$ \\
    $Z_{\mathrm min}$, $Z_{\mathrm max}$ & minimum/maximum $Z$ coordinate of LCFS \\
    $\kappa  = \frac{\left( {{Z_{{\rm{max}}}} - {Z_{{\rm{min}}}}} \right) } { \left( {{R_{{\rm{out}}}} - {R_{{\rm{in}}}}} \right) }$          & elongation   \\
    ${l_{\rm{i}}} = {{\bar B_{\rm{p}}^2}} / {{B_{\rm{a}}^2}}$          & normalized internal inductance   \\
    ${\beta _{\rm{p}}} = {{2{\mu _0}\bar p}} / {{B_{\rm{a}}^2}}$          & poloidal beta   \\
    $ W = \int_0^V {\frac{3}{2}p{\rm{d}}V'}$ & stored plasma energy \\
    $ q_0$, $q_{95}$ & safety factor at $\bar \psi = 0,\ 0.95$ \\
    \end{tabular}
\end{table}

>>>>

The final fourth step consists of reconstructing the equilibria form synthetic FREEBIE data using EFIT++ and VacTH. The reconstructions are then compared to the original equilibrium, focusing on global parameters and geometry. VacTH does not provide a full equilibrium but the plasma shape only (the target of VacTH is to provide such reconstructions in real time for a feedback control). Scans are performed over noise levels ($\epsilon$) and selected code parameters: $p'$ and $FF'$ polynomial degrees in EFIT++ ($n_{p'}$, $n_{FF'}$) and the number of harmonics ($n_P$, $n_Q$) in VacTH. The following quantities are used for the comparison.
\begin{table}[!h]
    \begin{tabular}{ll}
    $R_{\mathrm ax}$, $Z_{\mathrm ax}$ & $R,Z$ coordinates of the magnetic axis \\
    $R_{\mathrm in}$, $R_{\mathrm out}$ & inner/outer $R$ coordinate of LCFS at $Z=Z_{\mathrm ax}$ \\
    $Z_{\mathrm min}$, $Z_{\mathrm max}$ & minimum/maximum $Z$ coordinate of LCFS \\
    $\kappa  = \frac{\left( {{Z_{{\rm{max}}}} - {Z_{{\rm{min}}}}} \right) } { \left( {{R_{{\rm{out}}}} - {R_{{\rm{in}}}}} \right) }$          & elongation   \\
    ${l_{\rm{i}}} = {{\bar B_{\rm{p}}^2}} / {{B_{\rm{a}}^2}}$          & normalized internal inductance   \\
    ${\beta _{\rm{p}}} = {{2{\mu _0}\bar p}} / {{B_{\rm{a}}^2}}$          & poloidal beta   \\
    $ W = \int_0^V {\frac{3}{2}p{\rm{d}}V'}$ & stored plasma energy \\
    $ q_0$, $q_{95}$ & safety factor at $\bar \psi = 0,\ 0.95$ \\
    \end{tabular}
\end{table}

### 2014-09-09 Results.tex
first stats figures; n_p,q renamed to n_P,Q

\begin{figure*}
\centering   %\begin{center}
\hfill{}
\includegraphics[width=18cm]{figures/example_4275.pdf}
\hfill{}
%\end{center}
\caption{Contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 4275. EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$. VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_{\mathrm p} = n_{\mathrm q} = 5$.}
\label{fig:ex4275}
\end{figure*}

The second shot for the comparison is 6962, which has been chosen because Thomson scattering (TS) profiles are available. In Fig. \ref{fig:ex6962} we show reconstructions for more realistic equilibria and an artificial noise in the synthetic diagnostic signals. TS pressures were used in FREEBIE equilibria, which course no longer feature linear $p'$ and $FF'$ profiles. 
It is apparent that the reconstruction is not as good as in the previous case. Nevertheless, the plasma shape is well reconstructed with EFIT++ and VacTH, except for the last time slice in which VacTH yields too large plasma in the upper part.
$n_{\mathrm p} = n_{\mathrm q} = 4$ is used in this case as these values are minimum for reasonable VacTH results, while higher values are too sensitive to the input noise.
Expectedly, EFIT++ reconstruction with magnetic data only cannot reliably reconstruct kinetic plasma parameters, such as the stored energy or $q_0$. Rather unexpected is a relatively good agreement of $l_\mathrm{i}$. However, this agreement is compensated by a large error of $\beta_{\mathrm p}$ so that the quantity $\beta_{\mathrm p} + l_{\mathrm i}/2$ remain within a 10~\% error bar.

\begin{figure*}
\centering   %\begin{center}
\hfill{}
\includegraphics[width=18cm]{figures/example_6962_TS_noise.pdf}
\hfill{}
%\end{center}
\caption{Pressure profiles and contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 6962 with Thomson scattering pressure profiles. EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$. VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_{\mathrm p} = n_{\mathrm q} = 4$.}
\label{fig:ex6962}
\end{figure*}

@@

>>>>

\begin{figure*}
\centering   %\begin{center}
\hfill{}
\includegraphics[width=18cm]{figures/example_4275.pdf}
\hfill{}
%\end{center}
\caption{Contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 4275. EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$. VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 5$.}
\label{fig:ex4275}
\end{figure*}

The second shot for the comparison is 6962, which has been chosen because Thomson scattering (TS) profiles are available. In Fig. \ref{fig:ex6962} we show reconstructions for more realistic equilibria and an artificial noise in the synthetic diagnostic signals. TS pressures were used in FREEBIE equilibria, which course no longer feature linear $p'$ and $FF'$ profiles. 
It is apparent that the reconstruction is not as good as in the previous case. Nevertheless, the plasma shape is well reconstructed with EFIT++ and VacTH, except for the last time slice in which VacTH yields too large plasma in the upper part.
$n_{\mathrm p} = n_{\mathrm q} = 4$ is used in this case as these values are minimum for reasonable VacTH results, while higher values are too sensitive to the input noise.
Expectedly, EFIT++ reconstruction with magnetic data only cannot reliably reconstruct kinetic plasma parameters, such as the stored energy or $q_0$. Rather unexpected is a relatively good agreement of $l_\mathrm{i}$. However, this agreement is compensated by a large error of $\beta_{\mathrm p}$ so that the quantity $\beta_{\mathrm p} + l_{\mathrm i}/2$ remain within a 10~\% error bar. Notable are large errors (up to 40~\%) in the stored energy, even for the circular plasma, which are mainly caused by incompatible pressure profiles.

\begin{figure*}
\centering   %\begin{center}
\hfill{}
\includegraphics[width=18cm]{figures/example_6962_TS_noise.pdf}
\hfill{}
%\end{center}
\caption{Pressure profiles and contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 6962 with Thomson scattering pressure profiles. EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$. VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 4$.}
\label{fig:ex6962}
\end{figure*}

@@

\begin{figure*}
\centering   %\begin{center}
\hfill{}
\includegraphics[width=18cm]{figures/RZstats.pdf}
\hfill{}
%\end{center}
\caption{First row: EFIT++, second row: VacTH. Red: linear $p'$ and $FF'$ profiles, blue: TS pressure profiles, violet: $n_{p'}=2$ or $n_{FF'}=2$, TS profiles. Zero noise data are scattered for a better visibility.}
\label{fig:RZstats}
\end{figure*}

\begin{figure*}
\centering   %\begin{center}
\hfill{}
\includegraphics[width=18cm]{figures/kinetic_stats.pdf}
\hfill{}
%\end{center}
\caption{First row: $n_{p'}=n_{FF'}=1$, second row: either $n_{p'}=2$ or $n_{FF'}=2$. Red: linear $p'$ and $FF'$ profiles, blue: TS pressure profiles. Zero noise data are scattered for a better visibility.}
\label{fig:kinetic_stats}
\end{figure*}
